\tool: Programmable and Efficient Secure Two-Party Computation for Machine Learning

### 2018-08-07 ndss/impl.tex
nits

We use an off-the-shelf solver
(SeaHorn~\cite{seahorn}) to check that the array indices
are within bounds ($\models e < n$
in ({\sc {T-Read}}) and ({\sc{T-Write}}),
\figureref{compile}). We take the \tool source program and
translate it as an input C program to the solver. The solver takes less
than a minute on our largest benchmark to verify that all the array
accesses are in-bounds. This C program also enables
validation of \tool generated protocols via differential testing~\cite{mckeeman,frigate}.

>>>>

We use an off-the-shelf solver
(SeaHorn~\cite{seahorn}) to check that the array indices
are within bounds ($\Gamma \models e < n$
in ({\sc {T-Read}}) and ({\sc{T-Write}}),
\figureref{compile}). We take the \tool source program and
translate it as an input C program to the solver. The solver takes less
than a minute on our largest benchmark to verify that all the array
accesses are in-bounds. This C program also enables
validation of \tool generated protocols via differential testing~\cite{mckeeman,frigate}.
